FIXME

### 2013-09-03 writeups/proposal/proposal.tex
Tue writing
Former-commit-id: 00c9b2afe86bb4b50c9fd490922cd84cd7fb7bc0 [formerly 9b8ae1b422371e3a7c729594e60aef13c546eaa8]
Former-commit-id: d0117cc8ca159d6aa9c1cf6e4176e38474170202

@@

TODO: Sumarize Jones' model \cite{Jones2007}

@@

TODO: Summarize \cite{Sahlgren2008}

@@

TODO: Summarize \cite{Recchia2010}

>>>>

Vector-based represnetations compute chunk likelihoods by performing a correlation operation directly on the memory vectors.
Each memory vector can be thought of as a column on a context word x tag word co-occurrence matrix used for a Bayesian representation.
Further, the number of rows for a vector-based representation are fixed and set much smaller than the number of rows in the full word x tag co-occurrence matrix.
Since Bayesian representations have been shown to scale to over hundreds of millions of word x tag co-occurrences \parencite{Stanley2013}, the compressed vector-based representations should scale as well or better.

@@

\textcite{Jones2007} created the BEAGLE vector-based memory representation.
Each memory vector ($m_{j}$) is a summed representation of unordered and ordered word co-occurrences ($c_{j} + o_{j}$).
This model uses circular convoluation and inverse correlation as a way to encode and decode word order.
BEAGLE performed similar to LSA when trained on the TASA and tested on the TOEFL (55.6\% compared to 55.3\%).
BEAGLE with unordered context and word order was also more correllated to the WordNet synonym database than LSA (-.311 compared to -.165).
Further, it was shown that incorporating word-order information into the same representation resulted in minimal data loss (less than 1 percent of total predictive variance).
This model provided an efficient algorithm for using a single representation for unordered and ordered informaiton that showed performance similar to if not better than LSA.

@@

In order to represent word order information, a funciton must be used that converts the memory vectors for a set of words (``stack $\Phi$'') into a new uncorrelated environment vector.
The BEAGLE model uses circular convolution and inverse correlation as the encoding and decoding operations.
Howerver, that is certainly not the only operation that can generate new uncorrelated vectors from a set of memory vectors.
\textcite{Sahlgren2008} used a much simpler random permutation method for this operation.

Random permutatinos use a large sparse vector of zeros with a few ones in random locations as an environment vector for each of the words.
In order to create a new vector for a particular word that occurs one back ($\mathit{stack}^{-1}$), that word's environment vector ($e_{stack}$) is bit shifted to the left one position.
This produces a new environment vector for the combination of ``stack'' and the one back position that is uncorrelated with the original ``stack'' environment vector and all other environment vectors.
So if ``stack overflow'' occurred in a sentence, the one-back environment vector for ``stack'' would be added to the memory vector for ``overflow'' ($m_{overflow} = m_{overflow'} + e_{stack^{-1}}$).

A retrieval for a word following ``stack'' (``stack $\Phi$'') is done by creating a memory vector out of all information in context.
In this case, assume only a single piece of order information is available, that ``stack'' precedes the word to retrieve.
So the memory vector for context is the environment vector for one-back ``stack'' ($m_{context} = e_{stack^{-1}}$).
The memory vector for ``overflow'' will be correlated the highest with this context vector since it contains this vector.

@@

RP used the simplest permutation possible to create a new environment vector.
Performance is actually better than BEAGLE.
Computational efficiency is better as well.
Strong case for using RP over circular convulation for decoding / encoding.
TODO: Summarize \cite{Recchia2010}
